---
title: "TEST_SENSORS/DATA"
output:
  html_document:
    df_print: paged
---
```{r}
library(tidyverse)
```

```{r}
path <- "all_data3.csv"

df <- read_csv(
  path,
  col_names = c("s1", "s2", "s3", "s4", "gesture"),
  show_col_types = FALSE
)
```

```{r}
df <- df %>%
  mutate(
    s1 = as.numeric(s1),
    s2 = as.numeric(s2),
    s3 = as.numeric(s3),
    s4 = as.numeric(s4),
    gesture = as.factor(gesture)
  )
```

```{r}
df <- df %>%
  mutate(
    sample_id = cumsum(gesture != lag(gesture, default = first(gesture))) + 1
  )
```

```{r}
df <- df %>%
  group_by(sample_id) %>%
  mutate(t = row_number()) %>%
  ungroup()
```

```{r}
df_long <- df %>%
  pivot_longer(
    cols = c(s1, s2, s3, s4),
    names_to = "sensor",
    values_to = "value"
  )
```

```{r}
one_sample_per_gesture <- df_long %>%
  group_by(gesture) %>%
  filter(sample_id == first(sample_id)) %>%
  ungroup()
```

```{r}
one_sample_per_gesture_thin <- one_sample_per_gesture %>%
  group_by(gesture, sensor) %>%
  slice(seq(1, n(), by = 20)) %>%
  ungroup()
```


```{r}
gesture_list <- unique(one_sample_per_gesture_thin$gesture)

plot_list <- lapply(gesture_list, function(g) {
  one_sample_per_gesture_thin %>%
    filter(gesture == g) %>%
    ggplot(aes(x = t, y = value, color = sensor)) +
    geom_line(linewidth = 0.6) +
    facet_grid(sensor ~ ., scales = "free_y") +
    labs(
      title = paste("Signal shapes for gesture:", g),
      x = "Time step",
      y = "Sensor value"
    ) +
    theme_minimal(base_size = 14) +
    theme(legend.position = "none")
})
```

```{r}
plot_list[[1]]
plot_list[[2]]
plot_list[[3]]
plot_list[[4]]
plot_list[[5]]
plot_list[[6]]
plot_list[[7]]
plot_list[[8]]
plot_list[[9]]
plot_list[[10]]
```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
